---
title       : Hits and Run!!!
subtitle    : Data Visualization for All-Time Hits in MLB
author      : Mike Shih
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: libraries/nvd3}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 
## All-Time Hits in MLB
- The purpose of the project is to visualize all-time hits record in Major League Baseball.

- Lahman’s Baseball Database

- From 1871 to 2015

- Formats: csv, MS Access, SQL

- Database includes players' information (Master.csv) and career batting record (Batting.csv)

---

## Data Preparation - 1

- Covert middle names to abbreviation (names.R)

- Data proccessing (data_processing.R) 

1. merges Master.csv and Batting.csv
        
2. generates cumulative hits record, cumulative AB and seniority

3. removes the multiple data in the same year due to the transfering (remove_dup.R).   

---
## Data Preparation - 2

- User will input the maximum and minimun counts of hits on the sidebar panel. 

- The input values will pass to server.R and use funtion "careerhit" (in careerhit.R) to select players satisfied the criteria. 

---
## Ploting by rCharts NVD3

```{r, message=F, warning=F}
library(rCharts)
library(dplyr)
```

Players with hits over 3500.

```{r nvd3plot2, results = 'asis', comment = NA, message = F, echo = F}
library(rCharts)
library(dplyr)
source("careerhit.R")
Batting.data <- read.csv("./demo/Batting_Master.csv")
career_hit <- careerhit(Batting.data, 3500) 
Batting.all.total <- Batting.data[Batting.data$playerID %in% career_hit$playerID, ]

P1 <- nPlot(H_cum ~ yearID,
                data = Batting.all.total,
                group = "nameFull",
                type = "lineChart", 
                width = 650)

        P1$chart(showLegend = FALSE)
        P1$xAxis(axisLabel = "Year")
        P1$yAxis(axisLabel = "Cumulative Hits", width = 62)
        P1$chart(tooltipContent = "#! function(key, x, y, e){
                return '<P><h5><b>Name</b>: ' + e.point.nameFull + '<br>' +
                '<b>Year</b>: ' + e.point.yearID + '<br>' +
                '<b>Age</b>: ' + e.point.age + '<br>' +
                '<b>Seniority</b>: ' + e.point.seniority + '<br>' +
                '<b>Hits</b>: ' + e.point.H_cum + '<br>' +
                '<b>Batting Average</b>: ' + e.point.battingaverage + '<br>' +
                '</h5></P>'} !#")
P1

```

